Distance distribution by modes

### 2019-08-12 code/trips_analysis/trip_distance.Rmd
Use janitor to create grouped summarise

  library(tidyverse)
  library(ggthemes)
  library(plotly)
  library(knitr)

@@

```{r genTotalHistPlots, message = T, echo = F, warning = F}

@@

op <- ggplot(rd %>% filter(trip_distance < 51)) +
  aes(x = trip_distance, fill = cs) +
  geom_histogram(breaks = c(0:10,seq(11, 51, by = 5)), alpha=0.8, position="identity", aes(y = ..density..)) +
  labs(x = '') + 
  #geom_density(alpha = 0.4, color = 'lightgrey') +
  facet_wrap(vars(cs))

ggplotly(op)

@@

## Trip distance - density

```{r genTotalDensityPlots, message = T, echo = F, warning = F}

op <- ggplot(rd %>% filter(trip_distance < 50)) +
  aes(x = trip_distance, fill = cs) +
  labs(x = '') + 
  #geom_histogram(breaks = c(0:10,seq(11, 61, by = 5)), alpha=0.8, position="identity", aes(y = ..density..)) +
  geom_density(alpha = 0.8) +
  facet_wrap(vars(cs))

ggplotly(op)

```{r genPlots, message = T, echo = F, warning = F}

>>>>

  library(tidyverse)
  library(janitor)
  library(ggthemes)
  library(plotly)
  library(knitr)

@@

```{r genTotalHistPlots, message = F, echo = F, warning = F}

@@

rd <- rd %>% filter(trip_distance < 51) %>% mutate(category = cut(trip_distance, breaks = c(0:10,seq(11, 51, by = 5))))

# td <- rd %>% filter(!is.na(category)) %>% group_by(category, cs) %>% summarise(percentage = round(n() / nrow(.) * 100, 1))

td <- rd %>% filter(!is.na(category)) %>% tabyl(cs, category) %>% adorn_percentages("row")
td[, 2:ncol(td)] <- round(100 * td[, 2:ncol(td)], 1)
td <- reshape2::melt(td, by = cs)

op <- ggplot(td) +
     aes(x = variable, fill = cs, weight = value) +
     geom_bar() +
     scale_fill_hue() +
     theme_minimal() +
     facet_wrap(vars(cs)) + 
     labs(x = '', y = 'percentage (%)') +
     coord_flip()

# op <- ggplot(rd) +
#   aes(x = category, fill = cs) +
#   geom_bar() +
#   labs(x = '') + 
#   #geom_density(alpha = 0.4, color = 'lightgrey') +
#   facet_wrap(vars(cs), scales="free")  
ggplotly(op)

@@

<!-- ## Trip distance - density -->

<!-- ```{r genTotalDensityPlots, message = T, echo = F, warning = F} -->

<!-- op <- ggplot(rd %>% filter(trip_distance < 50)) + -->
<!--   aes(x = trip_distance, fill = cs) + -->
<!--   labs(x = '') +  -->
<!--   #geom_histogram(breaks = c(0:10,seq(11, 61, by = 5)), alpha=0.8, position="identity", aes(y = ..density..)) + -->
<!--   geom_density(alpha = 0.8) + -->
<!--   facet_wrap(vars(cs)) -->

<!-- ggplotly(op) -->

<!-- ``` -->

```{r genPlots, message = F, echo = F, warning = F}
